%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}



  \cventry
    {Artificial Intelligence Researcher and Engineer} % Job 
    {Research Assistant | Post-Doc} % Organization
    {London, United Kingdom} % Location
    {June. 2023 -- January. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I was the lead author and AI engineer for an international collaboration between the University of West London and Prince Sultan University in Riyadh, Saudi Arabia, I led a team of five researchers and developers. We developed a facial emotion recognition framework to enhance engagement in e-learning contexts. I designed a temporal algorithm using an augmented MobileNet to compute the dominant emotion from a sequence of frames, addressing transitional emotions and micro-expressions that typically reduce algorithm performance. The results and a preprint of the IEEE submission are available [here]. The manuscript is currently under review with IEEE.}
      \end{cvitems}
    }

%---------------------------------------------------------
 \cventry
    {System Analysis and Design} % Organization
    {Lecturer} % Job title
    {London, United Kingdom} % Location
    {February 2024 -- July. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As a lecturer for the undergraduate module in System Analysis and Design, I conducted both lectures and seminars. This course focused on software design principles and coding based on design specifications. Key topics included requirements gathering and analysis, stakeholder management, and the principles of the Unified Modelling Language (UML). I guided students in designing use cases, class diagrams, concept models, architectural models, sequence diagrams, and performing risk analysis.}
      \end{cvitems}
    }


%-------------------------------------------------------
 \cventry
  {Database Design, Research Methods, Object-Oriented Programming, Algorithms and Data Types} % Modules
  {Hourly Paid Lecturer} % Job Title
  {London, United Kingdom} % Location
  {2023 -- 2024} % Date(s)
  {
    \begin{cvitems}
      \item {Delivered lectures on database design and modelling, covering the creation of entity-relationship diagrams and data flow diagrams. Guided students in developing relational database systems and manipulating data using SQL queries using MySQL, Apex and SQLite}
      \item {Oversaw the Research Methods module, advising students on their theses, including project proposals, literature reviews, and methodologies.}
      \item {Instructed Object-Oriented Programming in Java, focusing on fundamental concepts such as inheritance, polymorphism and encapsulation.}
      \item {Taught web development, guiding students using HTML and Bootstrap for the front end, and PHP and MySQL for the backend.}
      \item {Covered Algorithms and Data Types using Python, teaching students how to use lists, queues, stacks and search trees in algorithms.}
      \item {Developed and provided solutions and coded examples on my GitHub repository to support student learning.}
    \end{cvitems}
  }
%---------------------------------------------------------
  \cventry
    {Pleotek} % Job 
    {Chief Technology Officer} % Organization
    {London, United Kingdom} % Location
    {2018 -- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Pleotek, established in 2018, aimed to enhance intelligent software solutions for the health and social care sectors in Northern Ireland, improving working conditions for nurses and healthcare professionals. I was responsible for overseeing the design of the company's software products, liaising with the development team in India, and applying for funding from venture capitalists and technology accelerators. In 2019, we were awarded £10,000 in funding from TechStart to support the initial development of the Pleotek ecosystem.}
      \end{cvitems}
    }
