
\cvsection{Publications}


\begin{cvparagraph}

\begin{enumerate}

\item \textbf{\textit{Pordoy, J.}}, Farman, H., Dicheva, N., Anwar, A., Nasralla, M. M., Rehman, I. U. (2024, Under Revision). Multi-Frame Transfer Learning Framework for Facial Emotion Recognition in e-Learning Contexts. \emph{IEEE Access}.


\item \textbf{\textit{Pordoy, J.}}, Jones, G., Matoorian, N., Zolgharni, M., Dadashiserej, D. (2023, Under Revision). Enhanced Non-EEG Multimodal Seizure Detection: A Real-World Model for Identifying Generalised Seizures Across The Ictal State. \emph{IEEE Journal of Biomedical and Health Informatics}.

\item \textbf{\textit{Pordoy, J.}}, Jones, G., Matoorian, N., Zolgharni, M., Dadashiserej, D. (2023, Under Revision). The Open Seizure Database Facilitating Research Into Non-EEG Seizure Detection. \emph{IEEE Journal of Biomedical and Health Informatics}.

\item Alajrami, E., Naidoo, P., Jevsikov, J., Lane, E., \textbf{\textit{Pordoy, J.}} et al. (2023). Deep Active Learning for Left Ventricle Segmentation in Echocardiography. In: Bernard, O., Clarysse, P., Duchateau, N., Ohayon, J., Viallon, M. (Eds.), \emph{Functional Imaging and Modeling of the Heart. FIMH 2023} (Vol. 13958, pp. 90-98). Springer, Cham.

\item \textbf{\textit{Pordoy, J.}}, Zhang, Y., Matoorian, N., Zolgharni, M. (2020). Predicting Epileptic Seizures with a Stacked Long Short-Term Memory Network. \emph{International Journal of Auto AI and Machine Learning}, 1(1), 93–108.

\item \textbf{\textit{Pordoy, J.}}, Zhang, Y., Matoorian, N., Zolgharni, M. (2020). Seizure Classification Using Person-Specific Triggers. \emph{EAI Endorsed Transactions on Collaborative Computing}, 18(3), 168650.

\end{enumerate}

\end{cvparagraph}

